CRUSE to Safe Cycling in Ireland

### 2023-10-06 paper.qmd
Port changes to .qmd, close #17 (#18)

-   Calculation of hundreds-of-thousands of routes, which is against the terms of service of the free API.
-   Making changes to the routing profiles, including allowing routing on trunk roads, which are not permitted in the default routing profiles.
-   Control over the version of OSM data being used for the routing, allowing regular updates to the route networks as OSM data is updated.

>>>>

-   Calculation of hundreds-of-thousands of routes, which is beyond the terms of service of the free API.
-   Making changes to the routing profiles, including allowing routing on trunk roads, which are sometimes avoided in the default routing profiles.
-   Control over the version of OSM data being used for the routing, allowing regular updates to the route networks as OSM data is updated.
